---
title: "Capstone"
author: "PRO"
date: "13 de octubre de 2017"
output: html_document
---

```{r, echo=FALSE, include=FALSE}
library(tm)
library(knitr)
library(ggplot2)
library(NLP)
library(quanteda)
dir<-"E:/COURSERA/Data Science/Course10-Capstone/"
dir1<-"E:/COURSERA/Data Science/Course10-Capstone/CORP"
#dir1<-"C:/Users/n040485/Documents/000_CAPSTONE/CORP"
dir2<-"E:/COURSERA/Data Science/Course10-Capstone/SAMPLE"
#dir2<-"C:/Users/n040485/Documents/000_CAPSTONE/CORP"
opts_knit$set(root.dir = dir1)
tsum <- data.frame()

```

## Intro
 
The first step in analyzing any new data set is figuring out.
This exercise uses the files named LOCALE.blogs.txt where LOCALE is the each of the four locales en_US, de_DE, ru_RU and fi_FI. The data is from a corpus called HC Corpora. See the About the Corpora reading for more details. The files have been language filtered but may still contain some foreign text.

The Original link of [data base](https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip).

We will use the English database but may consider three other databases in German, Russian and Finnish.




```{r, echo=FALSE,include=FALSE, warning=FALSE}

# Corpus
fullCorpus <- Corpus(DirSource(dir2), readerControl = list(language="en_US"))
fullcorpues<-corpus(fullCorpus)

```


## Tokenization

Preparing the information for the analysys is an essential task. For that purpose we need removing numbers, stopwords, and numbers. We would like to remove profanity world for our text too.

Tasks to accomplish

- Tokenization : identifying appropriate tokens such as words, punctuation, and numbers. Writing a function that takes a file as input and returns a tokenized version of it.
- Profanity filtering : removing profanity and other words you do not want to predict.


```{r, echo=FALSE, warning=FALSE}
# Profanity
profanity <- read.csv(paste(dir,"profanity_list.csv", sep=""), header=FALSE, stringsAsFactors=FALSE)
profanity <- profanity$V1

# Tokenizations
#Unigrams
tob<-dfm(fullcorpues, remove_numbers = TRUE,  remove_punct = TRUE, remove=profanity, toLower=TRUE)
gm1_top<- topfeatures(dfm(tob))
tob2 <-dfm(fullcorpues, remove_numbers = TRUE,  remove_punct=TRUE, toLower = TRUE, remove=c(profanity, stopwords("english")))
gm1bis_top<- topfeatures(dfm(tob2))
#Bigrams
gm2<-tokens(fullcorpues, remove_numbers = TRUE,  remove_punct = TRUE)
gm2<-toLower(gm2)
gm2<-removeFeatures(gm2,profanity)
gm2<- tokens_ngrams(gm2, n = 2L, skip = 0L, concatenator = " ")
gm2_top<- topfeatures(dfm(gm2))
#Trigrams
gm3<-tokens(fullcorpues, remove_numbers = TRUE,  remove_punct = TRUE)
gm3<-toLower(gm3)
gm3<-removeFeatures(gm3,profanity)
gm3<- tokens_ngrams(gm3, n = 3L, skip = 0L, concatenator = " ")
gm3_top<- topfeatures(dfm(gm3))
#Quatrigrams
gm4<-tokens(fullcorpues, remove_numbers = TRUE,  remove_punct = TRUE)
gm4<- tokens_ngrams(gm4, n = 4L, skip = 0L, concatenator = " ")
gm4_top<- topfeatures(dfm(gm4))
gm4<-toLower(gm4)
gm4<-removeFeatures(gm4,profanity)
```

```{r, results='asis', echo=FALSE, warning=FALSE}
#Unigrams graphics
#a
gf1 <- data.frame(word=names(gm1_top), count=gm1_top)
ggplot(gf1,aes(x=reorder(word, -count), y=count,fill=as.factor(word)))+ geom_bar(stat="identity")+ xlab('Count') + ylab('Words (unigrams)') + ggtitle('Most Common Unigrams Including Stop Words')
#b
gf1bis <- data.frame(word=names(gm1bis_top), count=gm1bis_top)
ggplot(gf1bis,aes(x=reorder(word, -count), y=count,fill=as.factor(word)))+ geom_bar(stat="identity")+ xlab('Count') + ylab('Words (unigrams)') + ggtitle('Most Common Unigrams non Including Stop Words') 
#Bigrams graphics
gf2bis <- data.frame(word=names(gm2_top), count=gm2_top)
ggplot(gf2bis,aes(x=reorder(word, -count), y=count,fill=as.factor(word)))+ geom_bar(stat="identity")+ xlab('Count') + ylab('Words (bigrams)') + ggtitle('Most Common Bigrams Including Stop Words') 
#Trigrams graphics
gf3bis <- data.frame(word=names(gm3_top), count=gm3_top)
ggplot(gf3bis,aes(x=reorder(word, -count), y=count,fill=as.factor(word)))+ geom_bar(stat="identity")+ xlab('Count') + ylab('Words (Trigrams)') + ggtitle('Most Common Trigrams Including Stop Words')
#Quatrigrams graphics
gf4 <- data.frame(word=names(gm4_top), count=gm4_top)
ggplot(gf4,aes(x=reorder(word, -count), y=count,fill=as.factor(word)))+ geom_bar(stat="identity")+ xlab('Count') + ylab('Words (Trigrams)') + ggtitle('Most Common Quatrigrams Including Stop Words')

```

# Next steps

